The Splashback Radius of Planck-SZ clusters

### 2019-02-14 Paper_v2/RSP_paper_new.tex
Smoothend plots and minor fixes
affiliation changed

\author{
Dominik Zürcher \altaffilmark{1, 2, 4}
Surhud More \altaffilmark{3, 1},
}
\affil{
$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583, Japan \\
$^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
$^{3}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India\\
$^{4}$ dominikz@phys.ethz.ch
}

@@

\section*{Acknowledgements}
DZ is grateful to Kavli IPMU for its hospitality during this research
project. SM is supported by a grant-in-aid by the Japan Society for
Promotion of Science (JSPS), grant number 16H01089. We acknowledge
useful discussions regarding this work with Benedikt Diemer, Neal
Dalal, Bhuvnesh Jain, Andrey Kravtsov, as well as participants of the
KITP UCSB workshop on the Galaxy-Halo connection in 2017. SM was
supported in part by the National Science Foundation under Grant No.
NSF PHY-1125915 during this workshop.

>>>>

\author{
Dominik Zürcher \altaffilmark{1, 2, 4}
Surhud More \altaffilmark{3, 1},
}
\affil{
$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583, Japan \\
$^{2}$Institute for Particle Physics and Astrophysics, Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
$^{3}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India\\
$^{4}$ dominik.zuercher@phys.ethz.ch
}

@@

\section*{Acknowledgements}
DZ is grateful to Kavli IPMU for its hospitality during this research
project. SM is supported by a grant-in-aid by the Japan Society for
Promotion of Science (JSPS), grant number 16H01089. We acknowledge
useful discussions regarding this work with Benedikt Diemer, Neal
Dalal, Bhuvnesh Jain, Andrey Kravtsov, as well as participants of the
KITP UCSB workshop on the Galaxy-Halo connection in 2017. SM was
supported in part by the National Science Foundation under Grant No.
NSF PHY-1125915 during this workshop. Further, we also thank the anonymous
referee for helpful comments and suggestions during the development of this 
manuscript.
